\documentclass[margin,line]{res}
\usepackage{color}
\definecolor{hyperlinks}{rgb}{0,0,0.5}
\definecolor{subtle}{rgb}{0.6,0.6,0.6}
\newcommand{\datesection}[1]{\section{\textnormal{\scriptsize \textcolor{subtle}{#1}}}}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=hyperlinks}

\usepackage[sc]{mathpazo}
\linespread{1.05}         % Palatino needs more leading (space between lines)
\usepackage[T1]{fontenc}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{\huge{Shrey Banga} \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
{\it E-mail:}  banga.shrey@gmail.com  & {\it Phone:}  (919)-448-8780 \\            
{\it Websites:} \url{cs.unc.edu/~banga/} & \url{www.github.com/milkbikis/} \\
\end{tabular}

\section{\sc Education}
\textsc{University \textit{of} North Carolina \textit{at} Chapel Hill}, Chapel Hill, NC, USA\\
\vspace*{-.1in}
\begin{list1}
\item[] Master of Science in Computer Science, May, 2013 (expected)
\end{list1}

\textsc{Indian Institute \textit{of} Technology Roorkee}, Roorkee, Uttarakhand, India\\
\vspace*{-.1in}
\begin{list1}
\item[] Bachelor of Technology in Electrical Engineering, May, 2009 \hfill {CGPA: 8.143/10}
\end{list1}

\section{\sc Experience}

\begin{format}
		\employer{l}\title{c}\location{r}\\
		\body\\
\end{format}

\datesection{June, 2013~-~Present}
\employer{\bf Quora Inc.}
\title{\em Software Engineer}
\location{Mountain View, California}
\begin{position}
Launched a number of experiments to improve growth metrics.
Built tools to understand and improve site speed.
Part of the group responsible for improving code-quality.
\end{position}

\datesection{May~-~August, 2012}
\employer{\bf Google Inc.}
\title{\em Software Engineering Intern}
\location{Mountain View, California}
\begin{position}
Created a tool for automatic regression alerts in Chrome's performance.
Fixed a WebKit bug, improving performance by a few percent.
Analyzed the effects of an alternative DNS alias selection strategy.
\end{position}

\datesection{January~-~August, 2011}
\employer{\bf Adobe Systems Inc.}
\title{\em Member of Technical Staff}
\location{NOIDA, India}
\begin{position}
Worked on improving and maintaining \textit{Camelot}, the PostScript printing engine.
\end{position}

\datesection{July~-~December, 2010}
\employer{\bf Center for Visual Information Technology}
\title{\em Project Engineer - Virtual Lab}
\location{IIIT Hyderabad}
\begin{position}
Designed a virtual lab for Computer Graphics, as part of a Government of India initiative for teaching sciences across colleges in India.
\end{position}

\datesection{June, 2009~-~April, 2010}
\employer{\bf Deloitte \& Touche}
\location{Hyderabad, India}
\title{\em Consultant}
\begin{position}
Helped implement a Biometric and Smart-Card authentication solution. \\
Performed vulnerability assessment and penetration testing on network infrastructure of several Fortune 500 companies
\end{position}

\datesection{May, 2008 to July, 2008}
\employer{\bf IBM India Software Labs}
\location{Bangalore, India}
\title{\em Software Engineering Intern}
\begin{position}
Created the EAR PlanCreator, an ajax-based plugin for quickly creating deployment plans for enterprise applications on Apache's Geronimo server.
\end{position}

\section{\sc Projects}
\datesection{August~-~December, 2011}
{\bf Computer Graphics}
\begin{list2}
\item {\em Raytracers}. created raytracers supporting common primitives, cameras, projections, transformations,
shading models, textures, reflection and refraction, global illumination, kD-tree acceleration and a scene file compiler.
\item {\em L-systems} parser and renderer for rendering fractals and other complex shapes.
\item {\em Force-directed layout} to display complex relationships of objects interactively in flash.
\end{list2}

\datesection{January~-~August, 2012}
{\bf Compilers}\\
{\em \href{https://github.com/milkbikis/miniJava-compiler}{miniJava compiler}} compiles a subset of Java into bytecode for a VM. Supports inheritance (instanceof, extends), overloading, constructors, loops, Strings and efficient code generation via short circuiting.

\datesection{January~-~August, 2011}
{\bf Android Development} \\
{\em DownloadAccelerator.} An Android app that accelerates downloads by splitting files into multiple parts and downloading them concurrently.

\datesection{September~-~December, 2011}
{\bf Chrome Extensions}
\begin{list2}
\item {\href{https://chrome.google.com/webstore/detail/mcpnehokodklgijkcakcfmccgpanipfp}{\em Google Mail Multi-Account Checker}} Shows multiple Gmail inboxes in a single pop-up, with common tasks such as delete, archive and mark as read. \textbf{Over 22,000 users}.
\item {\em Counter.} Counts your visits to websites and optionally blocks the page for a short time.
\end{list2}

\datesection{August, 2012}
{\href{https://github.com/milkbikis/powerline-bash}{Powerline for Bash}} A Python script that renders a beautiful and useful bash prompt
\datesection{May, 2011}
{\href{http://www.vim.org/scripts/script.php?script_id=3630}{IDSearch.vim}} A front-end to GNU ID utils which adds find-in-files support to {\em Vim} for large projects where grep isn't fast enough.

\datesection{January~-~May, 2008}
{\bf Machine Learning}
\begin{list2}
\item {\em Facial Expression Recognition} using a combination of Local Binary Patterns and SVM based classifiers.
%\item {\em Depth estimation from single monocular images.} Implemented a Gaussian Markov model for predicting depth from textural and monocular cues. Parameters of the model were learnt from training data and used to predict depth of a single test image. It was based on the paper, {\em 3-D Depth Reconstruction from a Single Still Image} by Ashutosh Saxena, Sung H. Chung and Andrew Y. Ng. \hfill {\bf August, 2008~-~May, 2009}
\end{list2}

\datesection{January~-~May, 2007}
{\bf Microprocessors}
\begin{list2}
\item {\em Intel 8085A Emulator.} An emulator for the Intel 8085A microprocessor with a modern GUI
\end{list2}

{\bf Web Design}
\begin{list2}
\item {\em Watch Out! News Agency.} A website for the students' news magazine of IIT Roorkee.
\item {\em Thomso'07 \& Srishti'07} Websites for several cultural and technical events at IIT Roorkee.
\end{list2}

\section{\sc Computer Skills} 
\textbf{Courses}
	\begin{list1}
		\item[]  Algorithm Analysis, Operating Systems, Data Structures, Compilers
	\end{list1}

\textbf{Languages}
	\begin{list1}
		\item[]  C, C++, Java, Python, JavaScript, HTML+CSS, shell script
	\end{list1}

\textbf{Platforms \& Tools}
	\begin{list1}
		\item[] Vim, unix commands, git, Eclipse, Visual Studio, \LaTeX{}
	\end{list1}

\section{\sc Co-curricular Activities}
{\bf Programming Contests}
\begin{list2}
\item Third in {\em Code Sangram}, an {\em IEEE (Roorkee chapter)} programming contest.
\item Participate regularly in programming contests on CodeChef, SPOJ, CodeJam, Hacker Cup etc.
\end{list2}

{\bf Software Development Section, Hobbies Club}, IIT Roorkee

Quizzing and Debating at {\bf Literary Section}, IIT Roorkee

{\bf Executive Editor \& Chief Web Coordinator}, {\em Watch Out! News Agency}, IIT Roorkee

{\bf Chief Web Designer, Thomso'07}, IIT Roorkee

\end{resume}
\end{document}
